### 2022-07-26 thesis/staticalg.tex
Grammar, improvements in figures, presentation

Given that $P$ is a parallelotope, all the states in $P$ can be expressed as a vector summation of anchor and scaled generators.
%
Let  $\langle v, g_1, \cdots, g_n \rangle$ be the generator representation of $P$.
%
The optimization problem given in Equation~\ref{eq:maxf} would then transform as follows.

@@

  There a few points worth noting here. First, by the discussion leading to Definition~\ref{def:halfspace_def}, the initial set would be the box $[0.79,0.8] \times [0.19, 0.2] \times 0$. This can be interpreted as initializing the model such that $79-80\%$ of the population is susceptible (not yet infected) with $19-20\%$ of the population is infected. As the simulation is beginning, no percentage of the population has recovered from the disease. Hence, the third parameter $r$ is set to zero.

  Second, since we only have the axis-aligned parallelotope in our initial bundle, the matrix $\T^Q$ will consist of only one row indicing the axis-aligned directions expressed as distinct rows in $\Lambda^Q$.

  \begin{figure}
  \label{fig:kaa_sir}
    \hspace*{-2.3cm}
    \includegraphics[width=1.3\textwidth]{figures/SIRProj.png}
    \caption{Projection of Reachable Set of SIR propagated 300 steps in time.}
  \end{figure}
\end{example}

\begin{example}

To include an example of a higher-dimensional non-linear system, we introduce the Phosporaley model. The Phosphoraley model describes a certain cellular regulatory system. It is captured by seven variables governed by the following discretized dynamics:
\begin{align}
  \begin{split}
      x^1_{k+1} &= x^1_k + ( -\alpha \cdot x^1_k + \beta \cdot x^3_k x^4_k)\cdot \Delta \\
      x^2_{k+1} &= x^2_k + (  \alpha\cdot  x^1_k - x^2_k)\cdot \Delta \\
      x^3_{k+1} &= x^3_k + ( x^2_k - \beta \cdot x^3_k x^4_k)\cdot \Delta \\
      x^4_{k+1} &= x^4_k + ( \beta \cdot x^5_k x^6_k - \beta \cdot x^3_k x^4_k)\cdot \Delta \\
      x^5_{k+1} &= x^5_k + ( -\beta \cdot x^5_k x^6_k + \beta \cdot x^3_k x^4_k)\cdot \Delta \\
      x^6_{k+1} &= x^6_k + ( \alpha\cdot  x^7_k - \beta \cdot x^5_k x^6_k)\cdot \Delta \\
      x^7_{k+1} &= x^7_k + ( -\alpha\cdot  x^7_k + \beta \cdot  x^5_k x^6_k)\cdot \Delta
  \end{split}
\end{align}
Here, we set the two parameters $\alpha,\beta$ as $\alpha=0.5$ and $\beta=5$. The discretization step is set to $\Delta =0.01$ and we propagate the reachble set for $S=300$ time steps. Additionally, the initial box is set to be $[1.00,1.01]^7 \times [-100, 100]$.
%
\begin{figure}[t!]
\label{fig:kaa_phos}
  \hspace*{-2.3cm}
  \includegraphics[width=1.3\textwidth]{figures/PhosporlayProjOn X_1, X_2, X_3.png}
  \caption{Projection of Reachable Set of the Phosporaley model propagated 300 steps in time.}
\end{figure}
%
Figure \ref{fig:kaa_phos} depicts the projection of the reachable set on the first three variables $x_1, x_2, x_3$. The relevant matrices are defined as:

@@

>>>>

Given that $P$ is a parallelotope, all the states in $P$ can be expressed as a vector summation of an anchor and a convex combination of generators.
%
Let  $\langle v, g_1, \cdots, g_n \rangle$ be the generator representation of $P$.
%
The optimization problem given in Equation~\ref{eq:maxf} would then transform as follows.

@@

  There a few points worth noting here. First, by the discussion leading to Definition~\ref{def:halfspace_def}, the initial set would be the box $[0.79,0.8] \times [0.19, 0.2] \times 0$. This can be interpreted as initializing the model such that $79-80\%$ of the population is susceptible (not yet infected) with $19-20\%$ of the population is infected. As the simulation is beginning, no percentage of the population has recovered from the disease. Hence, the third parameter $r$ is set to zero.
  %
  Second, since we only have the axis-aligned parallelotope in our initial bundle, the matrix $\T^Q$ will consist of only one row indicing the axis-aligned directions expressed as distinct rows in $\Lambda^Q$.
\end{example}

\begin{example}
To include an example of a higher-dimensional non-linear system, we introduce the Phosporaley model. The Phosphoraley model describes a certain cellular regulatory system. It is captured by seven variables governed by the discretized dynamics stated in Figure \ref{fig:phos_dynamics}:

\begin{center}
  \begin{equation*}
    \begin{split}
        x^1_{k+1} &= x^1_k + ( -\alpha \cdot x^1_k + \beta \cdot x^3_k x^4_k)\cdot \Delta \\
        x^2_{k+1} &= x^2_k + (  \alpha\cdot  x^1_k - x^2_k)\cdot \Delta \\
        x^3_{k+1} &= x^3_k + ( x^2_k - \beta \cdot x^3_k x^4_k)\cdot \Delta \\
        x^4_{k+1} &= x^4_k + ( \beta \cdot x^5_k x^6_k - \beta \cdot x^3_k x^4_k)\cdot \Delta \\
        x^5_{k+1} &= x^5_k + ( -\beta \cdot x^5_k x^6_k + \beta \cdot x^3_k x^4_k)\cdot \Delta \\
        x^6_{k+1} &= x^6_k + ( \alpha\cdot  x^7_k - \beta \cdot x^5_k x^6_k)\cdot \Delta \\
        x^7_{k+1} &= x^7_k + ( -\alpha\cdot  x^7_k + \beta \cdot  x^5_k x^6_k)\cdot \Delta
    \end{split}
  \end{equation*}
  \label{fig:phos_dynamics}
  \captionof{figure}{Discretized Dynamics of Phosphorlay Model.}
\end{center}
%
Here, we set the two parameters $\alpha,\beta$ as $\alpha=0.5$ and $\beta=5$. The discretization step is set to $\Delta =0.01$ and we propagate the reachble set for $S=300$ time steps. Additionally, the initial box is set to be $[1.00,1.01]^7 \times [-100, 100]$. Under these parameters, Figure \ref{fig:kaa_phos} depicts the projection of the reachable set on the first three variables $x_1, x_2, x_3$. The relevant matrices are defined as:

@@

\def \reachplotwidth {1.3}

\begin{figure}[h!]
  \hspace*{-2.4cm}
  \includegraphics[width=\reachplotwidth\textwidth]{figures/SIRProj.png}
  \caption{Projection of Reachable Set of SIR propagated 300 steps in time.}
  \label{fig:kaa_sir}
\end{figure}

\begin{figure}[h!]
  \hspace*{-2.4cm}
  \includegraphics[width=\reachplotwidth\textwidth]{figures/PhosporlayProjOn X_1, X_2, X_3.png}
  \caption{Projection of Reachable Set of the Phosporaley model propagated 300 steps in time.}
  \label{fig:kaa_phos}
\end{figure}
